### 2022-01-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@af265955124089f8d193e322f084cf61a3e86e08 🚀

\begin{figure}
\hypertarget{fig:biasmccinf}{%
\centering
\includegraphics{figures/bias_mcc_inf.png}
\caption{TODO}\label{fig:biasmccinf}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:biasrocpr}{%
\centering
\includegraphics{figures/bias_roc_pr.png}
\caption{TODO}\label{fig:biasrocpr}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:optimbias}{%
\centering
\includegraphics{figures/optim_bias.png}
\caption{TODO}\label{fig:optimbias}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:optimperf}{%
\centering
\includegraphics{figures/optim_perf.png}
\caption{TODO}\label{fig:optimperf}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:ecovalid}{%
\centering
\includegraphics{figures/valid_ensemble.png}
\caption{TODO}\label{fig:ecovalid}
}
\end{figure}

>>>>

\begin{figure}
\hypertarget{fig:biasmccinf}{%
\centering
\includegraphics{figures/bias_mcc_inf.png}
\caption{Response of MCC and Informedness to changes in the training set
bias for a fixed connectance (rows). Both of these values approach 1 for
a good model. Informedness is consistently high, and by contrast, MCC
increases with additional training set bias. Across all models, training
on a more connected network is easier.}\label{fig:biasmccinf}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:biasrocpr}{%
\centering
\includegraphics{figures/bias_roc_pr.png}
\caption{Response of ROC-AUC and PR-AUC to changes in the training set
bias for a fixed connectance (rows). ROC-AUC is consistently high, and
therefore not properly able to separate good from poor classifiers. On
the other hand, PR-AUC responds to changes in the training set. As in
fig.~\ref{fig:biasmccinf}, training on more connected networks is
easier.}\label{fig:biasrocpr}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:optimbias}{%
\centering
\includegraphics{figures/optim_bias.png}
\caption{Value of the optimal training set bias for the different models
and measures evaluated here, over a range of connectances. Informedness
was reliably maximized for balanced training sets, and kept this
behavior across models. For other measures, larger connectances in the
true network allowed lower biases in the training set. In a large number
of cases, ``over-correcting'' by having training sets with more than
half instances representing interactions would maximize the values of
the model performance measures.}\label{fig:optimbias}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:optimperf}{%
\centering
\includegraphics{figures/optim_perf.png}
\caption{When trained on their optimally biased training set, most
models were able to maximize their performance; this is not true for
decision tree, which had a very low PR-AUC, and to some extent for ridge
regression who had a slow increase with network connectance. The
ensemble had a consistently high performance despite incorporating poor
models.}\label{fig:optimperf}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:ecovalid}{%
\centering
\includegraphics{figures/valid_ensemble.png}
\caption{Visualisation of the models predictions for one instance of a
network prediction problem (shown in the ``Dataset'' panel). This figure
reveals how inspecting the details of the prediction is important:
indeed, although the performance measures hint at the fact that ridge
regression is mediocre, this figure reveals that it is making
predictions that correspond to a network with an entirely different
topology (namely, nested as opposed to diagonal).}\label{fig:ecovalid}
}
\end{figure}
